???

### 2018-05-12 inst/stable_line_proliferation/stable_line_proliferation.Rmd
adding stable line proliferation analysis

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable",
    "broom"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

@@

_Cell culture and confluency quantification_

10^4 PC3 cells, either miR34a asRNA overexpressing or WT, were seeded in 96 well plates. After attachment (3-4h) media was replaced with either RPMI (Gibco, life technology) (supplemented with 2mM L-glutamine, 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum) or HBSS. Cells were incubated in Spark Multimode Microplate reader for 48 hours at 37°C with 5% CO2 in a humidity chamber. Confluency was measured every hour.

@@

data <- getData("Figure 3c")

#normalize to first time point for control (Mock)
.normFun <- function(
  data,
  Confluency,
  Treatment,
  Biological.Replicate,
  Technical.Replicate,
  Cell.line
){
  bool1 <- data$Treatment == Treatment
  bool2 <- data$`Biological Replicate` == Biological.Replicate
  bool3 <- data$`Technical Replicate` == Technical.Replicate
  bool4 <- data$Time == 0
  bool5 <- data$`Cell line` == Cell.line
  bool <- bool1 & bool2 & bool3 & bool4 & bool5
  Confluency / pull(data, Confluency)[bool]
}

data <- data %>%
  group_by(Treatment, `Biological Replicate`, `Technical Replicate`, Time, `Cell line`) %>%
  mutate(
    normConfluency = .normFun(
      data,
      Confluency,
      Treatment,
      `Biological Replicate`,
      `Technical Replicate`,
      `Cell line`
    )
  ) %>%
  ungroup()

#calculate mean for each technical replicate
data <- data %>%
  group_by(Treatment, `Biological Replicate`, Time, `Cell line`) %>%
  summarize(
    techMean = mean(normConfluency)
  ) %>%
  ungroup()

#calculate stats
stats <- data %>%
  filter(Time != 0) %>%
  group_by(`Cell line`, Treatment, Time) %>%
  summarize(
    min = min(techMean),
    max = max(techMean),
    mean = mean(techMean),
    median = median(techMean),
    CI95l = t.test(techMean)$conf.int[1],
    CI95h = t.test(techMean)$conf.int[2]
  )

>>>>

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "miR34AasRNAproject",
    "broom"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

@@

_Cell culture and proliferation assay_

20^4 PC3 cells, either miR34a asRNA overexpressing or mock, were harvested and stained in 1 ml PBS with 5uM CellTrace Violet (!!!!) for 5min and subsequently seeded in 12 well plates. Time 0 measurements were taken once cells had attatched and treatments with RPMI (Gibco, life technology) 10% FBS, RPMI 0.1% FBS, or HBSS were simultaniously initiated in the remaining cells. RPMI mediums were all additionally supplemented with 2mM L-glutamine and 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum. Cells were incubated for the indicated times before harvesting and CellTrace Violet was quantified via flow cytometry (Sony SH800S Cell Sorter). Time 0 was performed in biological triplicate and technical duplicate whereas all other time points were performed in biological triplicates with one technical replicate.

@@

#data <- getData("Figure 3c")
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
path <- "data/stable_line_proliferation.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, path))))

#remove cells with negative fluorescence. Consider these 1224 cells artifacts 
data <- filter(data, Violet > 0)

##fix day0 data
#Since there are no treatments at time 0 and we want a corresponding Time 0 for 
#each of the treated samples, here we expand the Time 0 sample 3 times, one for 
#each treatment condition at later time points.
dataExpandT0 <- data %>% 
  filter(Time == 0) %>%
  bind_rows(., ., .) %>%
  mutate(Condition = c(
      rep("Normal", nrow(.) / 3),
      rep("0.1% FBS", nrow(.) / 3),
      rep("HBSS", nrow(.) / 3)
  )) %>%
  bind_rows(filter(data, Time != 0))

#calculate means of technical replicates in day0
#need to subsample first so that each condition has the same number of cells
set.seed(2387723)
data0 <- dataExpandT0 %>%
  filter(Time == "0" & Type == "stained") %>%
  select(-`FSC-A`, -`BSC-A`) %>%
  group_by(`Biological replicate`, `Technical replicate`, Condition, `Cell line`, Type) %>%
  sample_n(size = 5000) %>%
  ungroup() %>%
  arrange(`Cell line`, Condition, `Biological replicate`, `Technical replicate`, Violet) %>%
  mutate(
    `Technical replicate` = rep(c("Tr1", "Tr2"), nrow(.)/2),
    row = rep(1:(nrow(.) / 2), each = 2)
  ) %>%
  spread(`Technical replicate`, Violet) %>%
  rowwise() %>%
  mutate(Violet = mean(c(Tr1, Tr2))) %>%
  ungroup() %>%
  select(-(row:Tr2)) %>%
  bind_rows(., ., ., .) %>%
  mutate(Time = rep(c("0", "24", "48", "72"), each = nrow(.) / 4)) %>%
  arrange(Time, `Cell line`, Condition, `Biological replicate`, Violet)

#Randomly sample 5000 cells from each condition so that all samples have the 
#same number of cells
set.seed(2387723)
subData <- dataExpandT0 %>%
  select(-`FSC-A`, -`BSC-A`, -`Technical replicate`) %>%
  filter(Type == "stained" & Time != "0") %>%
  group_by(`Biological replicate`, Condition, `Cell line`, Type, Time) %>%
  sample_n(size = 5000) %>%
  ungroup()

#add back data from time point 0 with mean technical replicates calculated
#in addition, add a time point 0 corresponding to each cell and condition and
##calculate the difference for each cell from time 0
subData <- subData %>%
  bind_rows(filter(data0, Time == "0")) %>%
  arrange(Time, `Cell line`, Condition, `Biological replicate`, Violet) %>%
  add_column(day0Violet = data0$Violet) %>%
  mutate(violetNorm = Violet - day0Violet)

means <- subData %>%
  group_by(Time, `Cell line`, Condition) %>%
  summarize(
    mean = mean(violetNorm),
    CI95l = t.test(violetNorm)$conf.int[1],
    CI95h = t.test(violetNorm)$conf.int[2]
  )

subData %>%
  ggplot() +
  geom_smooth(aes(Time, violetNorm, colour = `Cell line`, group = `Cell line`), method = "lm") +
  geom_point(data = means, aes(Time, mean, colour = `Cell line`, group = `Cell line`)) +
  facet_wrap(~Condition) + 
  scale_y_continuous(breaks = c(0, -5000, -10000, -15000, -20000)) +
  theme_few()
